Fast Fujisaki-Okamoto transformation using encrypt-then-mac and applications to Kyber

### 2024-08-19 etm-transform/manuscript/main.tex
short discussion on probability of blind forgery

>>>>

    Note that $\epsilon_\mac$ quantifies the probability that an adversary can produce forgery for a unknown key without access to a signing oracles. While this is not a standard security definition for MAC, this probability is straightforward to estimate for some classes of MACs. As will be discussed in section \ref{sec:mac-performance}, with a Carter-Wegman-like one-time MAC instantiated with message length $L$ and a finite field with $F$ elements, such probability is at most $\epsilon_\mac \leq \frac{L+1}{F}$
